\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-23 trunk/arch.tex
minor typos and jpg to PDF converstion

\section{Planning and execution with \rx}
\label{sec:arch}

\subsection{Introductory concepts}
\label{sec:arch:intro}

@@

Systematic partitioned inference is a major contribution of
\rx. However that is not the focus of this chapter with details
covered in \cite{py10, rajan12}. Coupled interaction between planning
and the world on the other hand, has a significant implication on how
planning can be integrated in such frameworks. In this chapter we show
how using the \eu planner can be coupled to our framework by first
linking concepts in temporal planning with the \rx framework. Note
that in the following treatise, we call the formal semantic framework
of \rx as the 'agent'. Reactors constitute an entity within this agent
and are standalone blocks of inference. The scope, detail and number
of reactors are application specific and outside the scope of this
chapter.

@@

\subsection{The  \eu Deliberative Reactor}
\label{sec:arch:europa}

Within \rx, an instance of an \eu reactor comes with the sole purpose
to deliberate. A typical design of such a reactor takes its cues from
\texttt{IDEA} \cite{mus02, mus06} where both planning and execution
are based on a single unified model within a rich representation that
provides support for temporal inference. In \rx, the execution cycle
consists of two deliberation processes which are implemented as two
separate \eu solvers modifying the \emph{same} plan database.

@@

This assumption is problematic for situated agents in general and as
Fig. \ref{fig:tick-exec} shows, for \rx. Synchronization that tracks
state evolution can occur several times during reactor
deliberation. By making synchronization and deliberation share the
same plan we provide a solution that relaxes this static world
assumption. \texttt{IDEA} uses the same principle with all solvers in
an agent sharing the same plan for communicating environmental change
\cite{Dias:2003ua, mus06}. Specifically their {\em Reactive planner}
-- similar to our {\em synchronization} solver -- was often the solver
targeting the change at the execution frontier. 
% Although, none of the papers we found were detailing how this was
% handled in the architecture.
\cite{Dias:2003ua} states:

@@

This suggests a deliberate non overlap between {\em reactive planner}
and {\em deliberative planners} horizons. In \rx, and more
specifically in our \eu reactor the planning horizon of {\em
  synchronization} -- limited to the current tick -- is a subset of
the planning horizon of the deliberation steps -- starting at the
current tick and with an extent based on latency $\lambda$ and
look-ahead $\pi$ of the reactor. In this manner we avoid creating a
conflict between the deliberation and synchronization by controlling
the scheduling of these two process by the \rx agent.

@@

\subsubsection{Deliberation: Planning for  Evolving State}
\label{sec:arch:plan}

>>>>

\section{Planning and Execution with \rx}
\label{sec:arch}

\subsection{Introduction}
\label{sec:arch:intro}

@@

Systematic partitioned inference is a major contribution of
\rxe. However that is not the focus of this chapter with details
covered in \cite{py10, rajan12}. Coupled interaction between planning
and the world on the other hand, has a significant implication on how
planning can be integrated in such frameworks. In this chapter we show
how using the \eu planner can be coupled to our framework by first
linking concepts in temporal planning with the \rx framework. Note
that in the following treatise, we call the formal semantic framework
of \rx as the 'agent'. Reactors constitute an entity within this agent
and are standalone blocks of inference. The scope, detail and number
of reactors are application specific and outside the scope of this
chapter.

@@

\subsection{The  Deliberative Reactor}
\label{sec:arch:europa}

Within \rxe, an instance of an \eu reactor comes with the sole purpose
to deliberate. A typical design of such a reactor takes its cues from
\texttt{IDEA} \cite{mus02, mus06} where both planning and execution
are based on a single unified model within a rich representation that
provides support for temporal inference. In \rxe, the execution cycle
consists of two deliberation processes which are implemented as two
separate \eu solvers modifying the \emph{same} plan database.

@@

This assumption is problematic for situated agents in general and as
Fig. \ref{fig:tick-exec} shows, for \rxe. Synchronization that tracks
state evolution can occur several times during reactor
deliberation. By making synchronization and deliberation share the
same plan we provide a solution that relaxes this static world
assumption. \texttt{IDEA} uses the same principle with all solvers in
an agent sharing the same plan for communicating environmental change
\cite{Dias:2003ua, mus06}. Specifically their {\em Reactive planner}
-- similar to our {\em synchronization} solver -- was often the solver
targeting the change at the execution frontier. 
% Although, none of the papers we found were detailing how this was
% handled in the architecture.
\cite{Dias:2003ua} states:

@@

This suggests a deliberate non overlap between {\em reactive planner}
and {\em deliberative planners} horizons. In \rxe, and more
specifically in our \eu reactor the planning horizon of {\em
  synchronization} -- limited to the current tick -- is a subset of
the planning horizon of the deliberation steps -- starting at the
current tick and with an extent based on latency $\lambda$ and
look-ahead $\pi$ of the reactor. In this manner we avoid creating a
conflict between the deliberation and synchronization by controlling
the scheduling of these two process by the \rx agent.

@@

\subsubsection{Deliberation: Planning for  State Evolution}
\label{sec:arch:plan}

### 2012-02-23 trunk/europa.tex
heading changes based on Minh and discussion; also noted FP comments
minor typos and jpg to PDF converstion

\subsection{\eu Architecture}
\label{sec:europa:arch}

@@

\begin{figure}
\centering
\includegraphics[scale=0.5]{figs/EUROPA-Architecture.jpg}
\caption{\small The \eu Architecture}
\label{fig:europa-architecture}
\vskip+0.1cm
\end{figure}

@@

\subsection{Modeling}
\label{sec:europa:modeling}

\eu can ingest descriptions of models, plans and goals and thereby can
be applied to different domains and problems, simply by providing
different models and goals. Consequently the expressiveness of the
language for models, goals and plans is of great importance. For \eu,
\texttt{NDDL} allows the user to specify the different components of a
problem domain in a concise way. The main characteristics that make
\texttt{NDDL} a powerful tool for describing problem domains are:

@@

\subsection{Inference}
\label{sec:europa:inference}

In \eu, all the Variables and Constraints from a problem domain,
domain descriptions are kept inside the Constraint Reasoning Engine
(CRE).  The CRE provides a framework where any number of constraint
types can collaborate to perform inference and prune variable domains
using Bounds Propagation and Domain Reduction techniques. \eu uses a
Propagator pattern, in which a Propagator object keeps track of a set
of constraint instances of the same type and is responsible for
ensuring that whenever any variable changes or constraints are
introduced or dropped, all related variables are updated through
inference.

@@

\begin{figure}
\centering
\includegraphics[scale=0.35]{figs/europa-resource-envelopes.png}
\caption{\small Resource Envelopes computed by  \eu}
\label{fig:resenvelopes}
\vskip+0.1cm
\end{figure}

@@

\subsection{Search}
\label{sec:europa:search}

>>>>

\subsection{Architecture}
\label{sec:europa:arch}

@@

\begin{figure}
\centering
\includegraphics[scale=0.4]{figs/EUROPA-Architecture.pdf}
\caption{\small The \eu software architecture.}
\label{fig:europa-architecture}
\end{figure}

@@

\subsection{Modeling in \eu}
\label{sec:europa:modeling}

\eu can ingest descriptions of models, plans and goals and thereby can
be applied to different domains and problems, simply by providing
different models and goals. Consequently the expressiveness of the
language for models, goals and plans is of great importance. For \eue,
\texttt{NDDL} allows the user to specify the different components of a
problem domain in a concise way. The main characteristics that make
\texttt{NDDL} a powerful tool for describing problem domains are:

@@

\subsection{Automated Inference}
\label{sec:europa:inference}

In \eue, all the Variables and Constraints from a problem domain,
domain descriptions are kept inside the Constraint Reasoning Engine
(CRE).  The CRE provides a framework where any number of constraint
types can collaborate to perform inference and prune variable domains
using Bounds Propagation and Domain Reduction techniques. \eu uses a
Propagator pattern, in which a Propagator object keeps track of a set
of constraint instances of the same type and is responsible for
ensuring that whenever any variable changes or constraints are
introduced or dropped, all related variables are updated through
inference.

@@

\begin{figure}
\centering
\includegraphics[scale=0.2]{figs/europa-resource-envelopes.png}
\caption{\small Resource Envelopes computed by  \eu}
\label{fig:resenvelopes}
\vskip+0.1cm
\end{figure}

@@

\subsection{Search in \eu}
\label{sec:europa:search}

### 2012-02-23 trunk/setobook.tex
- added table of content  I was unable to embed it as pdf bookmarks due to apparent incompatibility of hyperref with our maketitle in svmult document class Insteed I just generated it before the document
minor typos and jpg to PDF converstion

\input{preamble}
\setcounter{secnumdepth}{-1}

@@

\title*{\textbf{\sc Towards Deliberative Control of Autonomous Robots}}
\author{\normalsize Kanna~Rajan\inst{1} \and Fr\'ed\'eric Py\inst{1}
  \and Javier Barreiro\inst{2}}
\institute{Monterey Bay Aquarium Research Institute, California
  \emph{\{Kanna.Rajan,fpy\}@mbari.org}
  \and
  NASA Ames Research Center, Moffett Field, California
  \emph{javier.barreiro@nasa.gov}}

@@

@@

Rajan and Py are funded by a block grant from the David and Lucile
Packard Foundation to MBARI. They thank their collaborators J. Ryan,
J. Harvey, R. Vrijenhoek and J. Bellingham at MBARI. In addition they
thank colleagues M. del Alto, D. Korsmeyer and S. Zornetzer at NASA
Ames who made \eu available as open source. The authors are indebted
to N. Muscettola for his ideas and early work at NASA Ames which forms
the basis of this work.

>>>>

\input{preamble}
\setcounter{tocdepth}{3}

@@

\title*{\textbf{\sc Towards Deliberative Control in Marine Robotics}}
\author{\normalsize Kanna~Rajan\inst{1} \and Fr\'ed\'eric Py\inst{1}
  \and Javier Barreiro\inst{2}}
\institute{Monterey Bay Aquarium Research Institute, California
  \emph{\{Kanna.Rajan, fpy\}@mbari.org}
  \and
  NASA Ames Research Center, Moffett Field, California
  \emph{javier.barreiro@nasa.gov}}

@@

\tableofcontents{}

@@

Rajan and Py are funded by a block grant from the David and Lucile
Packard Foundation to MBARI. They thank their collaborators John Ryan,
Julio Harvey, Jim Bellingham and Robert Vrijenhoek at MBARI. In
addition they thank colleagues Martha del Alto, David Korsmeyer and
Steven Zornetzer at NASA Ames who made \eu available as open
source. The authors are indebted to Nicola Muscettola for his ideas
and early efforts in Constraint-based Temporal Planning at NASA Ames
which forms the basis of this work.
